Model

### 2020-02-12 stats/model.Rmd
test run mixture model

# Model parameters

@@

### Pragmatic model

@@

## Model comparison

```{r}
d_model_comp <- data_comb%>%
  select(-age)%>%
  mutate(age = round(age_month,2),
         item = as.character(item))%>%
  select(alignment, item, age, correct)

test_prag <- readRDS("../saves/model_pred_prag.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_prag,"../saves/test_prag.rds")

test_global <- readRDS("../saves/model_pred_global.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_global,"../saves/test_global.rds")

test_flat <- readRDS("../saves/model_pred_flat.rds")%>%
  filter(iteration == 1286 | iteration == 7185)%>%
  mutate(age = round(age,2))

saveRDS(test_flat,"../saves/test_flat.rds")

d_model_comp <- data_comb%>%
  select(-age)%>%
  mutate(age = round(age_month,2),
         item = as.character(item))%>%
  select(alignment, item, age, correct)

xxg <- xxg %>%
  mutate(age = round(age,2))

sort(unique(d_model_comp$age))

sort(unique(xx$age))

y <- xx %>%
  right_join(d_model_comp)

tail(y)

bind_rows(

  xx %>%
    right_join(d_model_comp)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

xxf %>%
    right_join(d_model_comp)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "global",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like)

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global) %>%
  summarise(prag_vs_global = sum(prag_vs_global))

@@

# MAP based inverse predictions for ME data

```{r}
model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")

item_params<- model %>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)

global_params <- model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "parameters")%>%
    separate(value, into = c("int", "slope"),sep = ", ")%>%
    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
    gather(parameter, value, int, slope)

#### summaries

item_params_summary <- item_params %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by(token, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))
```

```{r}
# speak_opt_params <- speak_opt %>%
#   group_by(parameter)%>%
#   summarise(mode = estimate_mode(value),
#             uci = hdi_upper(value),
#             lci = hdi_lower(value))
#

inv_model_data <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, mode)%>%
  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
  mutate(speaker_optimality = so_int + so_slope * age,
         semantic_knowledge = plogis(int + slope * age))

@@

```{r}
invPred <- '
var allData = dataFromR.data

var priorProbs = [.5,.5]

var output = map(function(row){

    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)

    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])

}, allData)

output

'
```

```{r predictions pragmatic model ex 3 adults}
inv_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
  data =list(data = inv_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
inv_predictions <- inv_model_pred %>%
  separate(`0`, into = c("item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  dplyr::rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))
```

```{r}
# plot_model_pred <- model_pred_summary%>%
#   left_join(aoa_ratings) %>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa))

model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

model_plot
```

```{r}
p2 <- read_csv("../data/me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
  mutate(item = familiar)%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(item), mean_aoa))

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

```{r}
ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

## For comparison: GLMM for ME effect and data

```{r}
me_data <- read_csv("../data/me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))

# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
#                 data = me_data,
#                 family = bernoulli(),
#                 control = list(adapt_delta = 0.95),
#                 sample_prior = F,
#                 save_all_pars = TRUE,
#                 iter = 2000)

#saveRDS(me_model, "../saves/me_effect_model.rds")

me_model <- readRDS("../saves/me_effect_model.rds")

summary(me_model)

fixef <- as_tibble(fixef(me_model), rownames = "term")

ranef <-  ranef(me_model)

age_me_effect <- as_data_frame(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  tidyr::expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
         age = z_age+mean_age,
         item = familiar)%>%
  select(item, me_effect, age)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("GLMM")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

```{r}
ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
```

# MAP based Model predictions for combination

```{r}
# novelty data

novel_data <- read_csv("../data/novelty.csv")%>%
  mutate(age_num = age_num-min(age_num))

# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
#           data = novel_data, family = bernoulli(),
#           control = list(adapt_delta = 0.95),
#           sample_prior = F,
#           save_all_pars = F,
#           iter = 10000)
# 
# saveRDS(novel_bm, "../saves/novelty_model.rds")

novel_bm <- readRDS("../saves_old/novelty_model.rds")

summary(novel_bm)

novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
  select(term,Estimate)%>%
  spread(term, Estimate)

comb_model_data_con <- inv_model_data %>%
  mutate(nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = plogis(nov_int + age * nov_slope),
         alignment = "congruent")

comb_model_data_incon <- inv_model_data %>%
  mutate(nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = 1- plogis(nov_int + age * nov_slope),
         alignment = "incongruent")

comb_model_data <- bind_rows(
  comb_model_data_con,
  comb_model_data_incon)
```

```{r}
combPred <- '
var allData = dataFromR.data

var output = map(function(row){

    var prior = [row.prior, 1-row.prior]

    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)

    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])

}, allData)

output

'
```

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
) %>%
saveRDS("../saves/prag_model.rds")

comb_model_pred <- readRDS("../saves/prag_model.rds")

comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  dplyr::rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         source = "Model")

```{r}
p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

p_comb_model
```

```{r}
data_comb <- read_csv("../data/combination.csv") %>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa), 
         source = "Data")

p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "glm", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~alignment)+
  ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()+
  scale_fill_viridis_d()
```

```{r}
ggarrange(p_comb_model,p_comb_data, common.legend = T, legend = "right", nrow = 2, ncol = 1)
```

```{r}
#ggsave("../graphs/combination_model_data.pdf", width = 7, height = 7, scale = 1)
```

```{r}
p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  #geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)

p1 <- data_comb%>%
  group_by(source, alignment, item ,subage)%>%
  multi_boot_standard(col = "correct")

ggplot(p1, aes(x = subage+0.5, y = mean))+
  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, col = source))+
  facet_grid(alignment ~item)+
  #geom_line(aes(group=alignment,col = source))+
  #geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = source),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .2, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
  #geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = source), size = 1, alpha = 1)+
  #geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = source), alpha = .5) +
  theme_few()+
  labs(x ="Age", y = "Mutual Exclusivity effect")+
  scale_color_manual(name = "",
                     values = c("#117733", "#117733", "#CC6677"))+
  scale_fill_manual(values = c("#CC6677"))+
  guides(fill = F)+
  theme(legend.position = "bottom")

```{r}
ggsave("../graphs/data_model_talk_00.pdf", width = 12, height = 3.5, scale = 1.2)
```

@@

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         subage = factor(subage))%>%
  select(-a,-b,-n,-k)

binned_model <- comb_model_predictions %>%
  mutate(subage = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(subage, alignment, item)%>%
  summarise(model_mean = estimate_mode(me_effect),
            model_ci_lower = hdi_lower(me_effect),
            model_ci_upper = hdi_upper(me_effect))

cor_plot <- left_join(
  binnned_data,
  binned_model)

ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 2,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~subage)+
  theme_few() + 
  scale_colour_viridis_d(name ="Familiar object")
```

```{r}
ggsave("../graphs/talk_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
```

```{r}
ggarrange(
plot_item_params,
plot_global_params,
p_data_model, plot_global_sigma,
ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))

ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)

```{r}
model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("na", "me_effect"),sep = ",")%>%
  select(-na)%>%
  mutate(age = as.numeric(age),
         me_effect =as.numeric(str_remove(me_effect,"[)]")))

comb_model_pred_agg <- model_pred%>%
  group_by(Chain, alignment,item,age)%>%
  summarise(mean = estimate_mode(me_effect),
            uci = hdi_upper(me_effect),
            lci = hdi_lower(me_effect))%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         Chain = factor(Chain))

ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col), col = "black", fill = "grey",  method = "loess", se = F, alpha = .2, span = 2)+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(Chain ~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()+
  scale_fill_viridis_d()

```{r}
ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
```

# MAP based predictions with noise parameter

## Preparing data

```{r}
noise_model_data <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, mode) %>%
  left_join(read_csv("../data/combination.csv") %>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject,
         age = age_num - (min(age_num))))%>%
  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode),
    glob_sem_know_int = global_params_summary%>%filter(token == "global_sem", parameter == "int")%>%pull(mode),
         glob_sem_know_slope = global_params_summary%>%filter(token == "global_sem", parameter == "slope")%>%pull(mode),
         speaker_optimality = so_int + so_slope * age,
         semantic_knowledge = plogis(int + slope * age),
         global_semantic_knowledge = plogis(glob_sem_know_int + glob_sem_know_slope * age),
         nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))%>%
  select(item, alignment,age, speaker_optimality, semantic_knowledge,global_semantic_knowledge, prior, correct)

## Pragmatics model

```{r}
pragNoise <- '
var allData = dataFromR.data

var model = function(){

  var noise = uniform({a: 0, b: 1})

  var output = map(function(row){

    var prior = [row.prior, 1-row.prior]

    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)

    var noisyModelPredictions = addNoise(modelPredictions, noise)

    observe(noisyModelPredictions, row.correct)

    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])

}, allData)

 return extend(_.fromPairs(output), {noise: noise})

}
'
```

```{r predictions pragmatic model ex 3 adults}
prag_model_noise<- webppl(
  program_code = paste(rsaUtils, rsaModel, pragNoise , sep='\n'),
  data =list(data = noise_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
)

saveRDS(prag_model_noise, "../saves/prag_model_noise.rds")

prag_model_noise <- readRDS("../saves/prag_model_noise.rds")

# noise parameter
prag_model_noise_noise_param_summary <- prag_model_noise %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

>>>>

# Parameter free model

@@

@@

# Fully Bayesian model

item_params_fb <- readRDS("../saves/item_params_fb.rds")

global_params_fb <- readRDS("../saves/global_params_fb.rds")

item_sigma_fb <- readRDS("../saves/item_sigma_fb.rds")

#### summaries
item_params_summary_fb <- item_params_fb %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary_fb <- global_params_fb %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

```{r}
plot_item_params_fb <- ggplot(item_params_fb, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_item_params_fb
```

plot_global_params_fb <- ggplot(global_params_fb, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_global_params_fb
```

```{r}
plot_item_sigma_fb <- ggplot(item_sigma_fb, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()

plot_item_sigma_fb
```

```{r}
plot_sem_know_fb <- item_params_summary_fb%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$item)), .) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot(plot_sem_know_fb, aes(x = age+2, y= sem_know, col = item, group = item))+
  geom_line(size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "familiar object")
```

```{r}
model_pred_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")

plot_model_pred_prag_fb <- model_pred_prag_fb%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_prag_fb, aes(x=age+2,y = mean, col = alignment), size = 1)+
  geom_ribbon(data = plot_model_pred_prag_fb, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)

plot_model_prag_line_fb <- model_pred_prag_fb%>%
  filter(iteration %in% x_fb)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)

@@

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         age = factor(subage))%>%
  select(-a,-b,-n,-k)

cor_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age,
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model,alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

plot_cor_model_pred_fb <- cor_prag_fb %>%
  left_join(binnned_data)

ggplot(data = plot_cor_model_pred_fb,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")+
  guides(col = F)
```

# Mixture model

item_params_mm <- readRDS("../saves/item_params_mm.rds")

global_params_mm <- readRDS("../saves/global_params_mm.rds")

item_sigma_mm <- readRDS("../saves/item_sigma_mm.rds")

mixture_mm <- readRDS("../saves/mixture_mm.rds")

#### summaries
item_params_summary_mm <- item_params_mm %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary_mm <- global_params_mm %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

```{r}
plot_item_params_mm <- ggplot(item_params_mm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_item_params_mm
```

plot_global_params_mm <- ggplot(global_params_mm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

plot_global_params_mm
```

```{r}
plot_item_sigma_mm <- ggplot(item_sigma_mm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()

plot_item_sigma_mm
```

### Mixture

```{r}
plot_mixture_mm <- ggplot(mixture_mm, aes(x = p_informative, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("p_informative")+
  xlim(0,1)+
  theme_few()

plot_mixture_mm
```

```{r}
plot_sem_know_mm <- item_params_summary_mm%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$item)), .) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot(plot_sem_know_mm, aes(x = age+2, y= sem_know, col = item, group = item))+
  geom_line(size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "familiar object")
```

```{r}
model_pred_mm <- readRDS("../saves/model_pred_mm.rds")

plot_model_pred_mm <- model_pred_mm%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred_mm, aes(x=age+2,y = mean, col = alignment), size = 1)+
  geom_ribbon(data = plot_model_pred_mm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)

plot_model_prag_line_fb <- model_pred_prag_fb%>%
  filter(iteration %in% x_fb)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = model_pred_mm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)

@@

@@

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         age = factor(subage))%>%
  select(-a,-b,-n,-k)

cor_mix_mm <- readRDS("../saves/model_pred_mm.rds")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age,
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model,alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

plot_cor_model_pred_mm <- cor_mix_mm %>%
  left_join(binnned_data)

ggplot(data = plot_cor_model_pred_mm,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")+
  guides(col = F)
```
